KeysarMouseTracking.csv

### 2017-11-13 analysis/cogSci_analysis.Rmd
Plot cassette informativity rating distributions

>>>>

```{r}
library(ggthemes)
View(turkerRatings)

d <- turkerRatings %>%
  filter(objectSet == 3) %>%
  group_by(label,referent) %>% 
  mutate(avg = mean(response),
            med = median(response))

ggplot(d, aes(x = response)) +
    geom_histogram(binwidth = .1) +
    geom_vline(aes(xintercept=med)) +
    facet_grid(label ~ referent) +
    theme_few() +
    theme(aspect.ratio = .25, text = element_text(size=8))

ggsave(filename = '~/Downloads/cassette_informativity_ratings.png', height = 5)
```
